### 2010-02-18 StatusReport.tex
Added all of Bob's changes.

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\begin{document}

@@

    The standard model ran without convergence issues on the 2003 data for all
    rivers, but it did not converge on any of the 2004 data.  We simplified the
    model by eliminating E in an attempt to improve convergence, which worked
    for the 402m Whitewater River and 402m Zumbro River data.  Although none of
    the Mississippi River's 2004 data converged, we are still including
    estimates for the 402m Mississippi River data.

@@

    We decided not to run the models on the alternating plots. In our earlier
    analysis, we discovered that the main difference between alternating plots
    and all plots was that the alternating plots were more independent. When
    testing the standard model on spatially dependent simulated data, we found
    that the estimates were fairly accurate. The CAR model estimates were also
    fairly accurate on this simulated data, when it converged. Therefore, we
    decided to use the data that includes all plots because we feel that having
    the additional information from all plots is more important to the model
    than independence is.

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[hmargin=3cm, vmargin=3cm]{geometry}
\begin{document}

    \noindent{\textbf{Status Report for Otter Estimation Project \hfill Feb. 18,
    2010}

    \noindent{From: Chrisna Aing, Sarah Halls, Kiva Oken, Carleton College
    Senior Comps group} \\

    Recall that our "standard model," contains the following parameters:
    \(\psi\) (occupancy rate), \(\theta\) (probability of laying down a track,
    given occupancy), \(p\) (the detection probability for each observer; so \(1
    - p\) is the false negative rate), and \(E\) (the false positive rate for
    each observer).  We have also worked with a CAR model using the WinBUGS CAR
    installation.

@@

    The standard model ran without convergence issues on the 2003 data for all
    rivers, but it did not converge on any of the 2004 data.  We simplified the
    model by eliminating E (assuming no false positives) in an attempt to
    improve convergence, which worked for the 402m Whitewater River and 402m 
    Zumbro River data.  Although none of the Mississippi River's 2004 data 
    converged, we are still including estimates for the 402m Mississippi River 
    data.

@@

    We decided not to run the models on the alternating plots.  In our earlier
    analysis, we discovered that the main difference between alternating plots
    and all plots was that the alternating plots showed more independence in the
    data.  When testing the standard model on spatially dependent simulated
    data, we found that the estimates were fairly accurate.  The CAR model
    estimates were also fairly accurate on this simulated data, when it
    converged.  Therefore, we decided to use the data that includes all plots
    because we feel that having the additional information from all plots is
    more important to the model than independence is.
